Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_markdown.Rmd
Updating html

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
```

@@

```{r}
# s.df <- df %>% drop_na(s.id)

@@

library(fitdistrplus)

@@

```{r}
library(Hmisc)

>>>>

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(fitdistrplus)
library(Hmisc)
```

@@

```{r message=FALSE, warning=FALSE}
# s.df <- df %>% drop_na(s.id)

@@

@@
